An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2020-07-10 gas-adsorption/rsc-gas-ads-complete.tex
fix affiliation
shout out to cofs

%%%FOOTNOTES%%%
\footnotetext{\textit{$^{*}$~E-mail: pommerjo@oregonstate.edu}}
\footnotetext{\textit{$^{a}$~Department of Physics, Oregon State University, Corvallis, OR 97331, USA.}}
\footnotetext{\textit{$^{b}$~Department of Chemical, Biological, and Environmental Engineering, Oregon State University, Corvallis, OR 97331, USA. }}

@@

For a vehicle employing a porous material to store natural gas or hydrogen, the
(volumetric) \emph{deliverable capacity} of the gas is the primary
thermodynamic property that determines the driving
range~\cite{mason2014evaluating}. The adsorbed gas storage tank delivers the
gaseous fuel to the engine via an (assumed) isothermal pressure
swing~\cite{sircar2002pressure}. The deliverable capacity (see
Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage
pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest
pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set
deliverable capacity targets for both adsorbed methane and hydrogen storage and
delivery for vehicles. For methane, the Advanced Research Projects
Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$
per L of adsorbent at 298 K using a 65\ bar to 5.8\ bar pressure
swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of
progressive targets at five year intervals, with the ultimate target of 0.05 kg
H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a
minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the
emergence of highly tunable materials with large surface areas, such as
metal-organic frameworks~\cite{furukawa2013chemistry}, no porous material has
met these deliverable capacity targets.

>>>>

%%%FOOTNOTES%%%
\footnotetext{\textit{$^{*}$~E-mail: pommerjo@oregonstate.edu}}
\footnotetext{\textit{$^{a}$~Department of Physics, Oregon State University, Corvallis, OR 97331, USA.}}
\footnotetext{\textit{$^{b}$~School of Chemical, Biological, and Environmental Engineering, Oregon State University, Corvallis, OR 97331, USA. }}

@@

For a vehicle employing a porous material to store natural gas or hydrogen, the
(volumetric) \emph{deliverable capacity} of the gas is the primary
thermodynamic property that determines the driving
range~\cite{mason2014evaluating}. The adsorbed gas storage tank delivers the
gaseous fuel to the engine via an (assumed) isothermal pressure
swing~\cite{sircar2002pressure}. The deliverable capacity (see
Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage
pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest
pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set
deliverable capacity targets for both adsorbed methane and hydrogen storage and
delivery for vehicles. For methane, the Advanced Research Projects
Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$
per L of adsorbent at 298 K using a 65\ bar to 5.8\ bar pressure
swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of
progressive targets at five year intervals, with the ultimate target of 0.05 kg
H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a
minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the
emergence of highly tunable materials with large surface areas, such as
metal-organic frameworks~\cite{furukawa2013chemistry} and covalent organic 
frameworks~\cite{}, no porous material has met these deliverable capacity targets.
